### 2017-08-16 Tex_Dissertation/MSc_dissertation.tex
doneuntilp15

For the calculation of the top squark mass I made use of the TMVA package which provides a multivariate 
analysis platform in order (for this project) to make separation between the signal and the background. Two 
of them were empoyed, used and compared: the \textit{Boosted Descision Trees} (BDT) and the 
\textit{Gradient Boosted Descision Trees} (GBDT).

@@

Suppose we start with signal and background events described by a set of variables such as (in HEP) transverse 
momenta, missing energy, etc. Then TMVA sorts all events by each variable and we choose the one that gives the
best separation between signal and background. This is how the first node is made called root. Then, in the two branches 
that are made we repeat this procedure applying the best cut on each node until the splitting stops based on 
some criterion. That is how the terminal node is reached which is called leaf~\cite{hoecker2007tmva}.

@@

A way to circumvent this problem is to employ many different trees whose depth is small. They are called
weak learners. The classification of the event comes from the majority vote of these weak learners (boosting).
It is important to be noted that each tree is trainned with the same sample of input variables. That way not 
only we reach better results in the possible presence of statistical fluctuations but we also avoid the 
overtrainning of the trees.

>>>>

For the calculation of the top squark mass I made use of the TMVA package which provides a multivariate 
analysis platform in order (for this project) to make separation between the signal and the background. Two 
of them were employed, used and compared: the \textit{Boosted Descision Trees} (BDT) and the 
\textit{Gradient Boosted Descision Trees} (GBDT).

@@

Suppose we start with signal and background events described by a set of variables such as (in HEP) transverse 
momenta, missing energy, etc. Then TMVA sorts all events by each variable and we choose the one that gives the
best separation between signal and background. This is how the first node is made called root node. 
Then, in the two branches 
that are made we repeat this procedure applying the best cut on each node until the splitting stops based on 
some criterion. That is how the terminal node is reached which is called a leaf~\cite{hoecker2007tmva}.
This results into a descision tree where all nodes, from root to leaf node, separate (cut) the input
data into signal and background based on some criteria.

The "learning" phase where the nodes are created is called training phase. After this, where the 
nodes have been created, they are tested with a (not necessarily) new  data set in order to 
check their efficiency. This is called the testing phase.

@@

A way to circumvent this problem is to employ many different trees whose depth (number of nodes
of each tree) is small. 
They are called
weak learners. The classification of the event comes from the majority vote of these weak learners (boosting).
It is important to be noted that each tree is trained with the same sample of input variables. That way not 
only we reach better results in the possible presence of statistical fluctuations but we also avoid the 
overtrainning of the trees.
